---
title: "About"
output:
  html_document:
    includes:
      in_header: header.html
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error = FALSE, message = FALSE)
```

## 500 Women Scientists of Silver Spring, MD

<div class = "row">
<div class = "col-md-6">

```{r, fig.height=3, fig.width=3}
library(leaflet)
library(leafpop)
library(maps)
mapStates = map("state", fill = TRUE, plot = FALSE)
leaflet() %>%
  addTiles() %>%
    addMarkers(lng=-77.031586, lat=38.993062, group = "points")#,
             # popup=paste("<b>", members$Name, "</b> 
             #             <br/> ", members$Institution, 
             #             "<br/> ", ifelse(members$github %in% "", "", 
             #                              paste0("<a href = ", members$GitHub, "> GitHub </a> "))))

```

</div>

<div class = "col-md-6">
<br>
Welcome to the 500 Women Scientists Silver Spring Pod website! Our pod was established in _____  by Dr. Jane DiCosimo as a way for women scientists in the Silver Spring/D.C. Metro area and beyond to connect and find ways to share science with our communities and celebrate the contributions of women in science. Our pod is a part of [500 Women Scientists](https://500womenscientists.org/), a global collective of scientists focused on combating injustice and increasing equity in the sciences and society at large. 

The vision of 500 Women Scientists is to be the foremost organization for the transformation of leadership, diversity, and public engagement in science.


</div>

